### 2017-12-13 External Examination/Response To Referees.tex

			\item{\textbf{Page 25, second paragraph: Change ``On the other hand, an American..." to ``An American...", as you have mentioned hands before.
			\\\\}}
			The phrase ``On the other hand'' has been removed.
			\item{\textbf{Page 25: At this point you are talking about an American call, so if you are going to insist that $r(t) > 0$, then you also need to explicitly state that $q(t) > 0$, otherwise $S^*(t)$ will not exist.
			\\\\}}
			We have added the statement ``We start off by assuming that $q(t) > 0$ (otherwise, the American call will be equal to the European call).'' as we commence the American call option analysis on pg.~26 of the revised thesis.

			\item{\textbf{Page 26, after (2.13)--(2.15): Jump diffusion is not introduced until after (2.17), so I don't see the point in saying ``... by Jamshidian [60] \emph{for a pure diffusion case.}''; we are still talking about diffusion only cases at this point.
			\\\\}}
			The sentence fragment ``for a pure diffusion case'' has been removed.

			\item{\textbf{Page 27, after (2.18) and (2.19): What is the $\mathbb{E}$ operator taking expectations with respect to ($W_t$, $N_t$ or $Y$)?\\\\}}
			This expectation operator is taking expectations with respect to $Y$. This has been added to pg.~28 of the revised thesis.
			\item{\textbf{Page 27, after (2.19): You might want to point out that Merton also perfectly hedged the diffusion risk but \emph{ignored} the market price of the jump risk in order to get (2.20).
			\\\\}}
			This suggestion has been added to pg.~29 of the revised thesis right before (2.20) as ``The extension to include jumps allowed for the diffusion risk to be perfectly hedged but ignored the market price of the jump risk.''.

			\item{\textbf{Page 28, \S2.2.1: Many people might refer to the functions defined by (2.24) and (2.25) as the discounted, risk-neutral, probability-density functions for the SDE (2.1).
			\\\\}}
			The terminology \emph{Black-Scholes kernel} was used because we were explicitly using results from~\cite{Rodrigo2006, Rodrigo2013}, where the authors use this term to denote (2.24) and (2.25).

			\item{\textbf{Page 29, \S2.3: If you do not define the Mellin transform and its inverse in \S1.5, you really \emph{must} define both the Mellin transform and \emph{its inverse} here. You should also correct the (incorrect) statement here that $\xi \in \mathbb{R}$ here so that it reads $\xi \in \mathbb{C}$.
			\\\\}}
			The Mellin transform and its inverse are now both defined in \S2.3 in the revised thesis. We have also changed $\xi$ to belong in $\mathbb{C}$ instead of $\mathbb{R}$.

			\item{\textbf{Page 29, second displayed equation: I think the second equation should read
				$$
					(x^2f'')(x) = x^2f''(x),
				$$
				the superscript that should be on the $x^2$ term on the left-hand side seems to have gone missing. There is an inherent problem with kind of notation; how do you define $(x^2f'')(y)$? Is it
				$$
					(x^2f'')(y) = x^2f''(y) \quad \text{or} \quad (x^2f'')(y) = y^2f''(y)?		
				$$
				Judging by (2.29) you would choose the latter.
			\\\\}}
			To clear the ambiguity, we have refined the functions at the bottom of pg.~30 of the revised the thesis by setting function $\text{id} = \text{id}(x)$. Thus $(\text{id}\cdot f')$ and $(\text{id}^2 \cdot f'')$ can be defined such that
			$$
				(\text{id}\cdot f')(x) = x f'(x), \quad (\text{id}^2\cdot f'')(x) = x^2 f''(x),
			$$
			which should eliminate any notation disputes.

						\item{\textbf{Page 29, bottom:  It might be an idea to specify the sort of functions that $f$ and $g$ need to be in order that $f \ast g$ exists; see Titchmarsh, for example, for details.
			\\\\}}
			References have now been provided that allude to details for the conditions on $f$ and $g$ on pg.~31 of the revised thesis.

			\item{\textbf{Page 30, \S 2.4: Please insert the word \emph{standard} so that the first sentence reads ``Several properties of the \emph{standard} cumulative normal distribution $N$ ... ''.
			\\\\}}
			The word \emph{standard} has been inserted.

			\item{\textbf{Page 31 et seq:  Here you are definitely assuming that $\mathscr{M}^{-1}$ exists and that $\mathscr{M}^{-1}(f)$ is unique. This is why you need to explicitly write down a formula for $\mathscr{M}^{-1}$ and state that its action (on some class of functions) produces a unique result.
			\\\\}}
			The absence of the definition for the inverse Mellin transform has been addressed in previous comments.

			\item{\textbf{Page 36, \S3.1:  The line break for the title is not good. Please fix this if this is possible.
			\\\\}}
			The line break has been fixed.

			\item{\textbf{Page 31, \S3.1:  I would change ``... the European option with an underlying \emph{subjected} to jump-diffusion dynamics.'' to ``... the European option with an underlying that is \emph{described by} jump-diffusion dynamics.''
			\\\\}}
			The sentence now reads ``... the European option with an underlying that is \emph{described by} jump-diffusion dynamics.''
			\item{\textbf{Page 31, \S3.1:  Equation (3.1) would look better if the terminal condition appeared on a line by itself. \\\\}}
			The terminal condition has been moved to a line by itself.

			\item{\textbf{Page 37, first displayed equation: How do you know that $\mathbb{E}[Y^{-\xi}]$ exists?
			\\\\}}
			This has been addressed in a previous comment whereby we added the assumption that $\mathbb{E}[Y^{-\xi}]$ is convergent.

			\item{\textbf{Page 38, \S3.2:  I would suggest that you state that all of the derivations in the section are formal (otherwise someone might ask you to prove them).
			\\\\}}
			This has been appended to the beginning of \S3.2 of the revised thesis (pg.~40).

			\item{\textbf{Page 40, list of points:  In the first point the formula can only be applied if the distribution has a probability density function (otherwise (3.14) as it currently stands makes no sense).
			\\\\}}
			It has been previously mentioned that $f$ is the PDF of some random variable $Y$, thus we have already satisfied the condition that the distribution must have a valid PDF (see pg.~29 of the revised thesis under \S2.2).

			\item{\textbf{Page 46, after the last displayed equation: I would have written ``where $I$ is an interval with endpoints $a$ and $b > a$; the interval can be open, half-closed or closed''.
			\\\\}}
			This has been reworded to Dr Dewynne's suggestion on pg.~48 of the revised thesis.

			\item{\textbf{Page 46, after the last displayed equation:  The statement that $I$ is the interval $[K,\infty)$, after the first displayed equation on Page 47, seems redundant.
			\\\\}}
			This statement that $I$ is the interval $[K,\infty)$ has been removed.

			\item{\textbf{Page 50, \S3.6: I'm not sure what it is you're trying to say in the statement ``However, the integrals (3.11) are all real since the Mellin transform inversion has been performed in a different manner to [90] where the inversion was completed via a complex integral''. Is this a simple statement or fact? Are you claiming that real integrals are easier to compute than complex ones (if so, why didn't you compute the integrals in (3.14) for the double exponential and gamma pdfs)? What you didn't do, however, is show that the $F_n$ term always exists.
			\\\\}}
			For the statement in question, we wish to clarify that real integrals are in general easier to compute than complex integrals, but may not be necessarily easy to compute themselves. This is one of the key reasons why we decided to keep all our results in terms of real integrals versus complex integrals. The reason why we did not compute the integrals in (3.14) for the double exponential and gamma PDFs is because we merely wanted to demonstrate how our results would apply to these PDFs (which have results already found in literature). The purpose is more for comparison than anything else. The existence of $F_n$ has also been addressed in an earlier point of contention.

			\item{\textbf{Page 51:  Please give a reference to the ``recent empirical studies'' which suggest ``a better model for the asset process involves jumps following a double exponential distribution''.}
			\\\\}
			A reference has been provided and this sentence in question can now be found on pg.~52 of the revised thesis.

			\item{\textbf{Page 53, \S4.1.1:  Please give a definition of what it means for a function $\phi(x;x')$ to be homogeneous of degree one here (rather than half way down Page 54).
			\\\\}}
			This is now in \S4.1.1 on pg.~55 of the revised thesis.

			\item{\textbf{Page 56, top of page:  I assume you mean $u(x',t;x) = v(x,t;x')$, otherwise what is the point of defining $u$?
			\\\\}}
			This has been fixed on top of pg.~58 of the revised thesis.

			\item{\textbf{Page 73, (5.9): It might be a good idea to use a different symbol to $\mathscr{J}$, which has already been used earlier.
			\\\\}}
			We prefer to leave $\mathscr{J}$ in Eq.~(5.9) as it is for consistency of notation. In any case, we do not use the previous result Eq.~(3.13) here (i.e., different definitions).

			\item{\textbf{Page 74, \S5.1.2:  The ``lemma $n$'', ``Lemma $m$'' problem is particularly bad in this section (there is also an ``eq (3.18)'' on Page 75, whereas you usually write ``Eq.~(m.n)'').
			\\\\}}
			The mixture of lowercase and uppercase for the word \emph{lemma} has now been fixed to be consistent along with fixing the outlier ``eq'' to be ``Eq''.

			\item{\textbf{Page 81, 2nd line from the bottom:  I would change ``Similar to how we handled $I_{3,a}$'' to ``Similarly to how we dealt with $I_{3,a}$''.
			\\\\}}
			This has been changed on the bottom of pg.~83 of the revised thesis.

			\item{\textbf{Page 84, \S5.1.3: I think this section could be shortened. It is not really that different to \S5.1.2 and it sort of gives the impression of ``cut and paste''.
			\\\\}}
			\S5.1.3 was provided in full to complement \S5.1.2. This is because the formulas grew increasingly complicated that for the benefit of the reader, the details were provided in full so it would not be too overwhelming.

			\item{\textbf{Page 89, under (5.27): I don't understand what it means for a term to be \emph{mildly involved}.
			\\\\}}
			The phrase \emph{mildly involved} has been changed to \emph{rather complicated} on pg.~91 of the revised thesis.
			\item{\textbf{Page 100, \S5.4: I'm not sure what a ``favourable outcome'' is in the context of a numerical solution, nor am I sure what it means for a numerical result to be ``extremely credible''. I would also dispense with the word (?) ``renownedly''.
			\\\\}}
			``Favourable outcome'' is now ``positive results''; ``extremely credible'' is now ``to be accurate'' and the word (?) ``renownedly'' has been removed. These changes can be see on pg.~102 of the revised thesis.

			\item{\textbf{Page 101, (5.45):  But near the exercise boundary the American put is over twice as valuable as the European put. This shows that (5.45) is not always an accurate approximation. Presumably there is some limit in which (5.45) is accurate -- do you know what this limit is?
			\\\\}}
			The approximation (5.45) is to simplify the IDE for the free boundary $S^*(t)$ in (5.44). If this assumption was not implemented, then we would have no method of eliminating the $V_a$ term in (5.44). However, the end goal is still an option pricing formula $v_a$ for both an American put and call as seen in (5.17) and (5.29), respectively.

			\item{\textbf{Page 102, under the final displayed equation:  I think ``where we split the integral in $y$ at $y=1$ because this is the value that \emph{would} determine...'' would be more accurate if you changed from \emph{would} to \emph{could}.
			\\\\}}
			The word ``would'' is now ``could'' on pg.~104 of the revised thesis.

			\item{\textbf{Page 102:  I am slightly worried when you set $I_2$ to be zero because of cases such as shown in the figure provided. In particular, under your conditions you are always going to have $v_a^{\text{put}}(S^*(t),t) > v_e^{\text{put}}(S^*(t),t)$ and so imagine what happens if you chose $f(y)$ so that $f(y)/y$ has most of its mass near $y=1$.
			\\\\}}
			Once again, we wish to reiterate the purpose of setting $I_2$ to be equal to zero is similar to why we used (5.45) to obtain an approximate IDE for the free boundary $S^*(t)$. This to once again remove an additional $v_a$ term that would otherwise make the option pricing formulas implicit and thus inevitably much more complicated.

			\item{\textbf{Page 105, \S5.4.3:  This could be shortened as it is very similar to the main steps given in \S5.4.2
			\\\\}}
			The details in \S5.4.3 are provided in its entirety for the benefit of the reader since the equations in this section are quite complicated.

			\item{\textbf{Page 112, 2nd paragraph:  I would change the word \emph{instantiates} to \emph{uses} and eliminate the word \emph{best} from the first sentence.
			\\\\}}
			The sentence now reads ``One of the traditional FDMs used in options pricing uses a few change of variables in order to change the PDE (or PIDE) to resemble the typical heat equation.'' on pg.~113 of the revised thesis.

			\item{\textbf{Page 113, bottom line:  I would remove the word \emph{off} so that the sentence reads ``... as the asset price (denoted here by $x$) goes to infinity''.
			\\\\}}
			The word \emph{off} has been removed.

			\item{\textbf{Page 116, Figure 5.1:  This figure is not very useful as it doesn't show (a numerical approximation) to the actual free boundary (so we can't compare the solution of (5.48) with the actual free boundary).
			\\\\}}
			Figure 5.1 has now been edited such that a finite difference approximation to $S^*$ also appears along with the IDE approximation for $S^*$.

			\item{\textbf{Page 117, Page 5.2:  Where is $S^*(t)$ in the two frames of this figure? It is fairly clear that the approximate method doesn't do a very good job for $S< 6$ as the difference between the two methods is quite big there. Clearly some of this doesn't matter, because we know that the American put is equal to the payoff if $S < S^*(t)$, but it would be useful to be able to tell where that region was. It would also be helpful to put the financial parameters used to generate Figure 5.2 in the captions so the reader can easily see them.
			\\\\}}
			Figure 5.2 has now been adjusted to include a dotted vertical line indicating the value of $S^*(t)$ at $t=0$ where the profile for $S^*$ used was the approximate IDE.
			\item{\textbf{Page 120, \S6.2.1, between the final two displayed equations:  I think you mean that you assume that $v_c(y,T_1; K_2, T_2) > K_1$ for all $y > y_c^*$. I'm not sure what purpose the word ``greater'' is serving after $K_1$.
			\\\\}}
			The word ``greater'' has been removed.

			\item{\textbf{Page 126, \S6.3: Much of this has been already said earlier. 
			\\\\}}
			We wish to provide the details in full for the benefit of the reader.

			\item{\textbf{Page 126, \S6.3:  I would change the sentence ``The two auxiliary functions in (6.9) are the building blocks for \emph{all possible} financial payoffs in option pricing.'' so that it reads ``The two auxiliary functions in (6.9) are the building blocks for \emph{many} financial payoffs in option pricing.''
			\\\\}}
			The sentence now reads  ``The two auxiliary functions in (6.9) are the building blocks for \emph{many} financial payoffs in option pricing.'' on pg.~128 of the revised thesis.

			\item{\textbf{Page 127, \S6.4:  It's not entirely clear how you get from
				$$
					dS_t = [r(t)S_t - D(S_t,t)]dt + \sigma(t) dW_t,
				$$
				to (6.11).\\\\}}
			A reference has been provided in the same paragraph right above the displayed equation that leads into the details. We chose to omit them as adding them would not have added much to our content here.

			\item{\textbf{Page 127, \S6,4:  Also you need to say that $q_t < 1$, otherwise you get a negative share price from (6.11). 
			\\\\}}
			This assumption was made from the beginning on pg.~130 of the revised thesis with the sentence ``We call the proportion factor $q_d \in [0,1)$.'' which guarantees the factor is strictly less than $1$.

			\item{\textbf{Page 127, \S6.4:  Finally, you need to be a bit careful about saying that the first equation,
							$$
					dS_t = [r(t)S_t - D(S_t,t)]dt + \sigma(t) dW_t,
				$$
				here is ``general''.\\\\}}
				The phrase ``in general'' at the beginning of \S6.4 has been removed.

			\item{\textbf{I can't really see why you only do this for a single dividend yield. Certainly if you assume that $r$, $q$ and $\sigma$ are constants then you can use the result that $V(S,t)$ solves the Black-Scholes equation then so too does $V(\lambda S,t)$ for any $\lambda > 0$.
			\\\\}}
			By formulating the argument in this case of using some $\lambda > 0$ to represent the dividend yield, it may be possible, but we did not consider it for the purpose of this thesis as our primary goal was using the Mellin transform to show that an option pricing formula with one discrete dividend yield is able to be solved.
		\end{itemize}
\end{enumerate}

### 2017-12-13 UOW_thesis_template_v2-0/thesis_template/chapters/Preliminaries.tex
:art: Finished up all but one of Jeff's comments

\section{Mellin transform}
\label{subsec:mellin}
We now present the Mellin transform, which is going to be the mathematical technique that is a basis for all the work in this thesis. Suppose that $f : [0,\infty) \rightarrow \R$ is such that \textcolor{black}{$f = f(x)$}. The {\em Mellin transform}~$\hat f$ of $f$ at \textcolor{blue}{$\xi \in \mathbb{C}$} is defined as
\begin{equation*}
\hat f(\xi) =  \textcolor{black}{\M\left\{ f \right\}(\xi)} = \int_0^\infty x^{\xi - 1} f(x) \, \d x,
\end{equation*}
provided the integral converges at $\xi$. \textcolor{blue}{Now we denote the function id by $\text{id}(x) = x$. Then for each $x \in [0,\infty)$, define the functions~$(\text{id}\cdot f')$ and $(\text{id}^2 \cdot f'')$ by
\begin{equation*}
(\text{id}\cdot f')(x) = x f'(x), \quad (\text{id}^2\cdot f'')(x) = x^2 f''(x),
\end{equation*}
respectively.} It can be shown that \cite[pp. 362--363]{Myint1987}
\begin{equation}
\label{eqn:mellinDiv}
\M\{ xf'(x) \} = \widehat{x f'}(\xi) = -\xi \hat f(\xi), \quad \M\left\{ x^2f''(x) \right\} = \widehat{x^2 f''}(\xi) = \xi (\xi + 1) \hat f(\xi),
\end{equation}
assuming that $f$ satisfies
\begin{equation*}
\left. x^\xi f(x) \right\vert_0^\infty = 0, \quad \left. x^{\xi + 1} f'(x) \right\vert_0^\infty = 0.
\end{equation*}
\textcolor{blue}{To complement the Mellin transform expression, the inverse Mellin transform~\cite{Titchmarsh1948} is given by
\begin{equation*}
	f(x) = \M^{-1}\{\hat f(\xi)\} = \fr{1}{2\pi i} \int_{c-i\infty}^{c+i\infty} x^{-\xi}\hat f(\xi)  \, \d \xi,
\end{equation*}
where the contour used to get from $c - i\infty$ to $c + i\infty$ is the Bromwich contour since the Mellin transform is related to the two-sided Laplace transfrom through an exponential change of variables~\cite{Bracewell2000}}. Furthermore, we have
	\begin{equation*}
		\M\{ (f \ast g)(x) \} = (\widehat{f \ast g})(\xi) = \hat f(\xi) \hat g(\xi),
	\end{equation*}
where $f \ast g$ is the convolution of $f$ and $g$ defined to be
	\begin{equation*}
		(f \ast g)(x) = \int_0^\infty \fr{1}{y}f\left(\fr{x}{y}\right)g(y) \, \d y \quad \text{for all } x \geq 0.
	\end{equation*}
In addition to the Mellin transform and its properties, it was shown in~\cite{Rodrigo2006} that the Mellin transform of \eqref{eqn:optionKernelSoln} is
\begin{align}
		\label{eqn:mellinVkernel}
		\begin{split}
		\hat v(\xi,t) &= \hat \K(\xi,t,T) \hat \phi(\xi), \\
		\end{split}
	\end{align}
where 
\begin{equation}
	\label{eqn:KhatA}
 \hat\K(\xi,t,T) = e^{-\int_t^T p(\xi,\tau) \,  \d\tau},
 \end{equation} 
with
	\begin{equation}
		\label{eqn:Khat}
		p(\xi,\tau) = r(\tau) + \left( r(\tau) - q(\tau) - \fr{1}{2}\sigma(\tau)^2 \right)\xi - \fr{1}{2}\sigma(\tau)^2\xi^2.
	\end{equation}

>>>>

\section{Mellin transform}
\label{subsec:mellin}
We now present the Mellin transform, which is going to be the mathematical technique that is a basis for all the work in this thesis. Suppose that $f : [0,\infty) \rightarrow \R$ is such that \textcolor{black}{$f = f(x)$}. The {\em Mellin transform}~$\hat f$ of $f$ at \textcolor{blue}{$\xi \in \mathbb{C}$} is defined as
\begin{equation*}
\hat f(\xi) =  \textcolor{black}{\M\left\{ f \right\}(\xi)} = \int_0^\infty x^{\xi - 1} f(x) \, \d x,
\end{equation*}
provided the integral converges at $\xi$. \textcolor{blue}{Now we denote the function id by $\text{id}(x) = x$. Then for each $x \in [0,\infty)$, define the functions~$(\text{id}\cdot f')$ and $(\text{id}^2 \cdot f'')$ by
\begin{equation*}
(\text{id}\cdot f')(x) = x f'(x), \quad (\text{id}^2\cdot f'')(x) = x^2 f''(x),
\end{equation*}
respectively.} It can be shown that \cite[pp. 362--363]{Myint1987}
\begin{equation}
\label{eqn:mellinDiv}
\M\{ xf'(x) \} = \widehat{x f'}(\xi) = -\xi \hat f(\xi), \quad \M\left\{ x^2f''(x) \right\} = \widehat{x^2 f''}(\xi) = \xi (\xi + 1) \hat f(\xi),
\end{equation}
assuming that $f$ satisfies
\begin{equation*}
\left. x^\xi f(x) \right\vert_0^\infty = 0, \quad \left. x^{\xi + 1} f'(x) \right\vert_0^\infty = 0.
\end{equation*}
\textcolor{blue}{To complement the Mellin transform expression, the inverse Mellin transform~\cite{Titchmarsh1948} is given by
\begin{equation*}
	f(x) = \M^{-1}\{\hat f(\xi)\} = \fr{1}{2\pi i} \int_{c-i\infty}^{c+i\infty} x^{-\xi}\hat f(\xi)  \, \d \xi,
\end{equation*}
where the contour used to get from $c - i\infty$ to $c + i\infty$ is the Bromwich contour since the Mellin transform is related to the two-sided Laplace transfrom through an exponential change of variables~\cite{Bracewell2000}}. Furthermore, we have
	\begin{equation*}
		\M\{ (f \ast g)(x) \} = (\widehat{f \ast g})(\xi) = \hat f(\xi) \hat g(\xi),
	\end{equation*}
where $f \ast g$ is the convolution of $f$ and $g$ defined to be
	\begin{equation*}
		(f \ast g)(x) = \int_0^\infty \fr{1}{y}f\left(\fr{x}{y}\right)g(y) \, \d y \quad \text{for all } x \geq 0.
	\end{equation*}
\textcolor{blue}{The only conditions we require for $f$ and $g$ (see~\cite[chapter~2]{Titchmarsh1948} and \cite[chapter~11]{Poularikas2000}) is that they are both defined on the positive real axis $x \in (0,\infty)$.} In addition to the Mellin transform and its properties, it was shown in~\cite{Rodrigo2006} that the Mellin transform of \eqref{eqn:optionKernelSoln} is
\begin{align}
		\label{eqn:mellinVkernel}
		\begin{split}
		\hat v(\xi,t) &= \hat \K(\xi,t,T) \hat \phi(\xi), \\
		\end{split}
	\end{align}
where 
\begin{equation}
	\label{eqn:KhatA}
 \hat\K(\xi,t,T) = e^{-\int_t^T p(\xi,\tau) \,  \d\tau},
 \end{equation} 
with
	\begin{equation}
		\label{eqn:Khat}
		p(\xi,\tau) = r(\tau) + \left( r(\tau) - q(\tau) - \fr{1}{2}\sigma(\tau)^2 \right)\xi - \fr{1}{2}\sigma(\tau)^2\xi^2.
	\end{equation}
